Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-24 BN_discretizer_paper.tex
incorporating Yi-Chun's comments

MDL discretization requires that the network structure be known in advance, but can be incorporated into the structure learning process which would otherwise have required pre-discretized variables.
This approach alternates between traditional discrete structure learning and optimal discretization. \tim{Is this something this paper proposes or was this done with MDL before?}
Starting with some preliminary discretization policy, one first applys a structure learning algorithm to identify the locally optimal graph structure.
One then refines the discretization policy based on the learned network.
The cycle is repeated until convergence.

Results in this work suggest that the MDL method suffers from low sensitivity to discretization edges location and returns low numbers of discretization intervals on continuous variables.
\tim{We need another sentence to make this a \P.}

>>>>

MDL discretization requires that the network structure be known in advance, but can be incorporated into the structure learning process.
Simultaneous structure learning and discretization alternates between traditional discrete structure learning and optimal discretization.
Starting with some preliminary discretization policy, one first applys a structure learning algorithm to identify the locally optimal graph structure.
One then refines the discretization policy based on the learned network.
The cycle is repeated until convergence.

Results in this work suggest that the MDL method suffers from low sensitivity to discretization edge locations and returns low numbers of discretization intervals on continuous variables.
This is caused by the MDL's use of mutual information to rate discretization edges.
Mutual information, which is composed of empirical probabilities computed using event count ratios, varies less severely with the positions of discretization edges than the method proposed below.
